---
title: "posterpoller-workflow"
author: Candace Savonen
output: html_notebook
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(posterpoller)
```


## Set Up 

If for any reason you need to regenerate the same ids you will want to set the seed

```{r}
set.seed(1234)
```

1. Create a Googlesheet that has the `poster_title` and `presenter_name` as columns: 

[See example here](https://docs.google.com/spreadsheets/d/12aomFyT0zEHNmpyCQoGdDh16P-bRp4Pkt4PCCrU7gYY/edit#gid=0)

Keep this `poster_googlesheet` link handy. 

```{r echo = FALSE}
googlesheets4::read_sheet(
    ss = "https://docs.google.com/spreadsheets/d/12aomFyT0zEHNmpyCQoGdDh16P-bRp4Pkt4PCCrU7gYY/edit#gid=0"
  )
```


2. Authorize posterpoller package to access files in your Google Drive. 

```{r eval = FALSE}
posterpoller::authorize()
```

3. Make a new poll with `make_poll()` function. 

```{r}
form_info <- make_poll(new_name = "New Poster Poll")
```

4. In the opened window of the new poll you created, click the vertical "..." for `More options` and choose "Get prefill link".

<img src ="resources/prefill_link_button.png" width=300px">

In this screen, put `{poster_id}` and `{poster_title}` and `{presenter_name}` as the responses. 

<img src ="resources/entries.png" width=300px">

Then click "Get Link" on the bottom.

There will be a tiny pop up at the bottom left that says "COPY LINK". Click that button. 

<img src ="resources/copy_link.png" width=200px">

Keep this `prefill_url` handy for the next step. 

4. Run generate `generate_poster_ids()` function by putting your `prefill_url` and `poster_googlesheet` into this function. 

Your links should look something like this: 

```{r eval = FALSE}
prefill_url <- "https://docs.google.com/forms/d/e/1FAIpQLSeyLuU0f-2ow2kI62QWR4dIcr7hBib51yhnDThBvUNOL0z-RQ/viewform?usp=pp_url&entry.38519462=%7Bposter_id%7D"
poster_googlesheet <- "https://docs.google.com/spreadsheets/d/12aomFyT0zEHNmpyCQoGdDh16P-bRp4Pkt4PCCrU7gYY/edit#gid=0"
```

Now we can run the function. 

```{r eval = FALSE}
generate_poster_ids(prefill_url = prefill_url,
                    poster_googlesheet = poster_googlesheet)
```

```{r}
sessionInfo()
```
