---
title: "post_session_tally"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{post_session_tally}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(posterpoller)
```

## About the score calculation

We ended up using this calculation for the score:
```
log2(num_votes + 1)*mean_score*distinct_domain
```
The mean highest rating was important but this made sure that the number of votes was weighted. People often vote 10s for all posters which means we needed a way to differentiate mean scores of 10.

`distinct_domain` is obtained from the email addresses and indicates the unique domains that voted for the poster (and is a proxy for institution membership of the voter).

The `distinct_domain` aspect makes sure that there is no "home court advantage" for anyone nor is it just "who has the most friends" at the conference. Basically if individuals from a number of universities all agreed your poster was good that was more valuable then if all your votes came from the same institution (which is likely your lab or colleagues).

```{r, include = FALSE}
library(magrittr)
```

## Setting up the vote response sheet

In your poster voting google form that you set up previously you will need to go to `Responses` > `Link to sheet`. Then you will put the URL for that where we have `<voting_googlesheet_URL>` below.

```r
votes_df <- googlesheets4::read_sheet(<sheet_link here>) %>%
  janitor::clean_names() %>%
  dplyr::rename(email = email_address_conference_registration_email_address_must_be_used,
                score = on_a_scale_of_1_to_10_how_would_you_rate_the_clarity_of_scientific_communication_in_this_poster_presentation)
```

Account for spaces sometimes being trimmed by some QR code readers:

```r
votes_df <- votes_df %>%
  dplyr::mutate(presenter_name = gsub(" ", "", trimws(presenter_name)),
                poster_title = gsub(" ", "", trimws(poster_title)))
# Minor formatting fix.
votes_df$poster_id <- unlist(votes_df$poster_id)

```

People may accidentally vote twice. We will keep the most recent vote only.

```r
all_df <- all_df %>%
  dplyr::distinct(poster_id, email, .keep_all = TRUE) %>%
  readr::write_csv("raw_data.csv")

all_df
```

Now tally various types of scores. We'll save to a CSV file.

```r
tally_df <- all_df %>%
  #
  tidyr::separate(email, sep = "@", into = c("email_name", "domain")) %>%
  dplyr::group_by(poster_id, presenter_name) %>%
  dplyr::summarize(mean_score = mean(score),
                   sd = sd(score),
                   num_votes = dplyr::n(),
                   distinct_domain = length(unique(domain)),
                   score = log2(num_votes + 1)*mean_score*distinct_domain) %>%
  dplyr::arrange(desc(distinct_domain), desc(score)) %>%
  readr::write_csv("final_scores.csv")
```


## Plots

Distribution of number of votes per poster.

```r
library(ggplot2)
  ggplot2::qplot(x = tally_df$num_votes, geom = "density") +
    ggplot2::xlab("Number of votes")
```

Distribution of score.
```r
  ggplot2::qplot(x = tally_df$score, geom = "density") +
    ggplot2::xlab("score")
```

## Session info

For reproducibility purposes.

```{r}
sessionInfo()
```
