---
title: "set_up"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{set_up}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(posterpoller)
```

## Set Up

If for any reason you need to regenerate the same ids you will want to set the seed

```{r}
set.seed(1234)
```

1. Create a Googlesheet or CSV file that has the `poster_title` and `presenter_name` as columns:

[See example here](https://docs.google.com/spreadsheets/d/12aomFyT0zEHNmpyCQoGdDh16P-bRp4Pkt4PCCrU7gYY/edit#gid=0)

You can start by declaring the URL to your googlesheet or the file path to your local csv file. 

```{r}
poster_googlesheet <- "https://docs.google.com/spreadsheets/d/12aomFyT0zEHNmpyCQoGdDh16P-bRp4Pkt4PCCrU7gYY/edit#gid=0"
```
OR 
```{r}
poster_csv <- example_poster_data_file_path()
poster_csv
```

2. Make a copy of this google form: https://docs.google.com/forms/d/1x2QwyztUMaL0mVFRN4Ds6fThnpJJ_z-FzLvfvHlbZ7M/edit

3. Change the description and title as needed.

4. In the opened window of the new poll you created, click the vertical "..." for `More options` and choose "Get prefill link".

<img src ="resources/prefill_link_button.png" width=300px>

In this screen, put `{poster_id}` and `{poster_title}` and `{presenter_name}` as the responses respectively.

<img src ="resources/entries.png" width=300px>

Then click "Get Link" on the bottom.

There will be a tiny pop up at the bottom left that says "COPY LINK". Click that button.

<img src ="resources/copy_link.png" width=200px>

Copy and paste this URL below to declare as an R object. It should look something like the example below. We'll need this for the next step.

```{r eval = FALSE}
prefill_url <- "https://docs.google.com/forms/d/e/1FAIpQLScLJ3TU6YBsoXWYe8UQRwnkqBBPmbUmth8hnNvjOka_ntuOoA/viewform?usp=pp_url&entry.38519462=%7Bposter_id%7D&entry.2095768008=%7Bpresenter_name%7D&entry.1154882998=%7Bposter_title%7D"
```

5. Run generate `generate_poster_ids()` function by putting your `prefill_url` and `poster_key_file` into this function. `poster_key_file` will be either your Googlesheet's URL or a local csv file path. 

Now we can run the function.

```{r eval = FALSE}
generate_poster_ids(prefill_url = prefill_url,
                    poster_file_key = poster_csv,
                    dest_folder = "qr-codes",
                    pdf_compile = "all-qr-codes")
```

## Session info

For reproducibility purposes.

```{r}
sessionInfo()
```
